Centrality and Activity for Envolving Networks

### 2013-06-24 network-science/paper.tex

\begin{center} \begin{tikzpicture} \begin{axis}[ 
	thick,
	xmax=5, ymax=1,
	axis line style=very thick,
	axis x line=bottom,
	axis y line=left,
	xlabel={$z$},
	ylabel={evolving activity},
        legend pos=outer north east
] 
	\addplot[color=blue!50!black,samples=300,domain=-20:-0.001] {exp(ln(10)*(1/x))}; 
	\addplot[color=green!50!black,samples=300,domain=-20:-0.001] {exp(ln(100)*(1/x))}; 
	\addplot[color=red!50!black,samples=300,domain=-20:-0.001] {exp(ln(1000)*(1/x))}; 
	\legend{$\mu=10$,$\mu=100$,$\mu=1000$};
	\end{axis} \end{tikzpicture} 
\end{center}

>>>>

\begin{center} \begin{tikzpicture} \begin{axis}[ 
	thick,
	width=0.6\textwidth,
	x=1cm/4,
	xmax=10, ymax=1,
	axis line style=very thick,
	axis x line=bottom,
	axis y line=left,
	xlabel={$z$},
	ylabel={evolving activity},
] 
	\addplot[color=blue!50!black,samples=300,domain=-40:-0.001] {exp(ln(10)*(1/x))}; 
	\addplot[color=green!50!black,samples=300,domain=-40:-0.001] {exp(ln(100)*(1/x))}; 
	\addplot[color=red!50!black,samples=300,domain=-40:-0.001] {exp(ln(1000)*(1/x))}; 
	\legend{$\mu=10$,$\mu=100$,$\mu=1000$};
	\end{axis} \end{tikzpicture} 
\end{center}
